% Import Packages
\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{listings}
\usepackage[letterpaper, margin=2cm]{geometry}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{underscore}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{amsmath}

% Set syntax highlighting for python
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{pythonstyle}{
    language=Python,
    backgroundcolor=\color{backcolour},
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,
    breaklines=true,
    captionpos=b,
    keepspaces=true,
    columns=flexible,
    numbers=none,
    numbersep=5pt,
    showspaces=false,
    showstringspaces=false,
    showtabs=false,
    tabsize=4,
    upquote=true,
    frame=single
}
\lstdefinestyle{nocoloring}{
    keywordstyle=\color{black},
    commentstyle=\color{black},
    stringstyle=\color{black}
}

\lstset{style=pythonstyle}

\newcommand{\inputpython}[1]{ \lstinputlisting[language=Python]{ #1 }}
\newcommand*\lsin{\lstinline[language=Python]}

\setlength{\parindent}{0pt}
% \setlength{\parskip}{\baselineskip}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[R]{\thepage}
\fancyhead[L]{Mossman: Project 1}

\title{ECE 464: Fault Simulation}
\author{Jaden Mossman}
\date{October 2022}

\begin{document}
    \maketitle
    \tableofcontents

    \newpage
    \section{Introduction and Workload Reflection}
        \begin{enumerate}[label=\Alph*.]
            \item Which modules does your program achieve?
            
            My Program achieves all the specified modules, including ``Single TV, single fault'', ``Single TV, all faults'', ``Fault coverage of 1-10 TVs'', and ``Supporting unknown input''.
            
            \item Explain how you implement each of the following functionalities:
            \begin{enumerate}[label=\roman*.]
                \item Circuit simulation.
                \item Fault simulation.
                \item Full fault list generation.
            \end{enumerate}
            
            \item How many hours in total did you take to finish this project? What are your main contributions to this project? How did you help your team member?
            
            I spent approximately 12 hours on this project. My main contributions were everything because I did not have any team members. I helped my team by doing everything.
            
        \end{enumerate}

    \section{Screenshots of Test Cases}
        \newcommand{\testtxt}[1]{\lstinputlisting[style=nocoloring]{report/testouts/#1.txt}}
        \begin{enumerate}[label=\Alph*.]
            \item Single TV, single fault
            \begin{enumerate}[label=\roman*.]
                \item Show 2 example runs for hw1.bench, one with a tv detecting a fault, one with a tv not detecting a fault.
                \testtxt{A.i.1}
                \testtxt{A.i.2}
                
                \item Show 2 example runs for c17.bench, one with tv=00000, and a fault of your choice, one with tv=11111, and fault 22-10-0 (node 22 with input 10 stuck at 0).
                \testtxt{A.ii.1}
                \testtxt{A.ii.2}

                \item Show 1 example run for c432.
                \testtxt{A.iii}

                \item Show 1 example run for c1355.
                \testtxt{A.iv}

            \end{enumerate}

            \item Single TV, all faults
            \begin{enumerate}[label=\roman*.]
                \item Show 1 example run for hw1.bench
                \testtxt{B.i}

                \item Show 1 example run for c17.bench
                \testtxt{B.ii}

                \item Show 1 example run for c499.bench
                \testtxt{B.iii}

                \item Show 1 example run for c880.bench
                \testtxt{B.iv}

            \end{enumerate}
            
            \item Fault coverage of 1-10 TV
            \begin{enumerate}[label=\roman*.]
                \item Show a table or plot for c2670.bench
                \testtxt{C.i}

                \item Show a table or plot for c7552.bench
                \testtxt{C.ii}
                
            \end{enumerate}
            
            \item Unknown input support - use hw1.bench and c880.bench to show your results.
        \end{enumerate}

    \section{Link to repl}
        \url{https://replit.com/@JadenMossman/ECE464Project1}
    
    \newpage
    \section{All Files Used}
        \newcommand{\FileUsed}[1]{\section*{ #1 }\lstinputlisting[language=Python]{ #1 }}
        \FileUsed{main.py}
        \FileUsed{circuit.py}
        \FileUsed{node2.py}
        \FileUsed{state5.py}

\end{document}
